Robots Showing Emotions: Emotion Representation with no bio-inspired Body

### 2016-11-27 JournalInteractionStudies/Parts/conclusions.tex
Add files via upload

	\item It is possible to convey emotions through changes in angular and linear velocity of a non-bio-inspired body also without changes in the body shape. This lesson opens the door to the inclusion of simple "emotion" to robotic platforms that are not required to have bio-inspired characteristics, but have to interact with humans.

@@

	\item Emotions come as a reaction to an event. Therefore, just showing uncorrelated movements to the participants is not going to support the study of the expression of all the emotions. For example, the action Fear was well perceived by the participants when the robot get far from them, as they were inducing it.

	\item Giving the participants the possibility to write their interpretation of the robot's movements was not going to be helpful to assess what emotion they thought the robot was conveying during case studies. Although there are plenty of procedures that have been proposed to determine the emotion that a person could be thinking at (e.g., SAM), they could just be used in a controlled environment where the experimenter could spend long periods of time with the participant. This is not the case of exhibitions where people would agree to stop just for a couple of minutes. On the other side, exhibitions make it possible to collect a large number of subjects representative of a varied population.

>>>>

	\item It is possible to convey emotions through changes in angular and linear velocity of a non-bio-inspired body also without changes in the body shape. This lesson opens the door to the inclusion of simple emotion representation to robotic platforms that are not required to have bio-inspired characteristics, but have to interact with humans.

@@

	\item Emotions come as a reaction to an event. Therefore, just showing uncorrelated movements to the participants is not going to support the study of the expression of all the emotions. For example, the emotional expression of \textit{fear} was well perceived by the participants when the robot moved far from them, as they felt they were inducing it.

	\item Giving the participants the possibility to write their interpretation of the robot's movements was not going to be helpful to assess what emotion they thought the robot was conveying during case studies. Although there are plenty of procedures proposed to determine the emotion that a person could be thinking at (e.g., SAM), they could be used only in a controlled environment where the experimenter could spend long periods of time with each subject. This is not the case of exhibitions where people would agree to stop just for a couple of minutes. On the other side, exhibitions make it possible to collect a large number of subjects representative of a varied population.

### 2016-11-27 JournalInteractionStudies/Parts/introduction.tex
Add files via upload

The expression of emotion in robots is becoming a quite important issue to implement robots able to interact with people in a social context. Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs. Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting on emotion expressions that could not be broadly used in most platforms.
There are applications where the shape of the robot is constrained by functional needs, such as in the case of home cleaners, lawn mowers, transporters, flying drones, and many others. In all these cases, emotions can be expressed with the only available body, exploiting movement features.

@@

The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments in robotics~\cite{Sharma2013} and suggested by psychologist~\cite{Russell2003}.

>>>>

The expression of emotion in robots is becoming a quite important issue to implement robots able to interact with people in a social context. Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs. Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting in emotion expressions that could not be broadly used in most platforms.
There are applications where the shape of the robot is constrained by functional needs, such as in the case of home cleaners, lawn mowers, transporters, flying drones, and many others. In all these cases, emotions can be expressed with the only available body, exploiting movement features.

@@

The obtained results show that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments in robotics~\cite{Sharma2013} and suggested by psychologists~\cite{Russell2003}.
